Yoghurt under stress

### 2015-01-20 plis_figures.tex
fig:patterns

>>>>

\begin{figure*}
	\tikzsetnextfilename{patterns}
	\input{fig_plis/patterns.pgf}
	\caption{Patterns corresponding to the samples of Table~\ref{tab:data}. (a-d) increasing cell thickness. (e-f) larger solid content. (g-i) increasing glycerol content. All pictures are stitching of fluorescent microscopy images except (c,e) which are details of reflected light macroscope images. Scale is common to all panels (scale bar \SI{1}{\milli\metre}). Length of arrows correspond to the measured primary wavelength.}
	\label{fig:patterns}
\end{figure*}
